{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-17 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes all

@@

@@

            % STRONG CONVEXITY DEFINITION

@@

            \begin{definition}[strong convexity]\label{def:necoara-scnvx}

@@

            Then it's not hard to imagine the following natural relaxation of the above conditions. 

@@

            \begin{theorem}[Hierarchy of weaker S-CNVX conditions]\label{thm:q-cnvx-hierarchy}

@@

        \subsection{Characterizing Q-SCNVX functions with Hoffman's Error bound}
            Necoara et al. \cite{necoara_linear_2019}

@@

                Under Assumption \ref{ass:necoara-2019-settings}, assume that $f$ is Q-CNVX with $\mu_f, L_f$, then the sequence that satisfies Definition \ref{def:projg-alg} has a linear convergence rate. 

@@

                    \item $f \in \mathbb Q$ satisfying Q-Growth, a consequence of Q-CNVX by Theorem \ref{thm:q-cnvx-hierarchy}. 

>>>>

    \section{Convexity results}

@@

        \begin{definition}[strong convexity]\label{def:scnvx}
            Let $\alpha \ge 0$. 
            $f: \RR^n \rightarrow \RR^n$ is $\alpha$ strongly convex if and only if $f - \alpha/2\Vert \cdot\Vert^2$ is a convex function. 
            The definition doesn't exclude convex functions. 
        \begin{theorem}[strong convexity equivalences]\label{thm:scnvx-eqvs}
            Let $f:\RR^n \rightarrow \RR$ be $\alpha \ge 0$ strongly convex then, it is equivalent to 
                (\forall \lambda \in [0, 1])\; 
                f(\lambda x + (1 - \lambda)y) \le \lambda f(x) + (1 - \lambda)f(y) -\alpha\frac{\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2.

@@

            % STRONG CONVEXITY

@@

            \begin{theorem}[strong convexity characterized via Bregman Divergence]\label{thm:breg-div-scnvx}

@@

            Then, it's not hard to imagine the following natural relaxations of the above condition. 

@@

            \begin{theorem}[Hierarchy of weaker SCNVX conditions]\label{thm:wcnvx-hierach}

@@

        \subsection{Characterizing Q-SCNVX functions with Hoffman's error bound}
            Back in 1955, Hoffman \cite{hoffman_approximate_1952} determined the existence of an upper bound for the distance of a point to a polyhedron can be bounded by the constraint violations of the point, uniformly. 
            Let's adopt $[\cdot]_+$ as the notation for projecting on $\RR^n_+$. 
            Necoara re-introduce the bound, the following theorem phrase that upper bound in the exact same way, but with only the Euclidean norm. 
            \begin{theorem}[Polyhedral Hoffman Error bound]
                Let $A \in \RR^{p \times n}, C \in \RR^{m\times n}$. 
                Given non-empty polyhedron: $P := \{x \in \RR^n : Ax = b, Cx \le d\}$, there exists a constant $\theta(A, C) > 0$ such that 
                    (\forall x \in \RR^n)\; \dist(x | P) \le \theta(A, C)\left\Vert
                            Ax - b \\ [Cx - d]_+
            The constant $\theta(A, C)$ is referred to as the Hoffman constant in the literature. 
            There are two notable generalization of the inequality. 
            Güler et al. \cite{guler_approximations_1995} found a representation of the Hoffman constant via singular values of sub matrices that defines the polyhedron. 
            Burke and Tseng \cite{burke_unified_1996} unified the analysis for the Hoffman constant and extend it to the context of general cone over a sublinear convex function, and more. 
            It's important to note at this point that the exact value of $\theta(A, C)$ is very difficult to obtain in practice. 
            Let's go back to Necoara \cite{necoara_linear_2019}. 
            The following theorem stated their use of the Error bound condition to capture a class of Q-SCNVX function. 
            \begin{theorem}[Q-SCNVX and Hoffman's error bound]\label{thm:q-scnvx-hffmn-eb}
                Let $X := \{S \in \RR^n: Cx \le d\}$ be non-empty, $g:\RR^m \rightarrow \RR$ be a $\sigma_g$ strongly convex and, $L_g$ Lipschitz smooth function. 
                Let $A \in \RR^{m\times n}$ be a nonzero, $C \in \RR^{m\times n}$. 
                Then $f(x):= g(Ax)$ is Q-SCNVX with $L_f = L_g\Vert A\Vert^2$, $\kappa_f = \sigma_g/\theta(A, C)^2$. 
                $X\neq \emptyset$ determines a non-empty set of minimizers $X^+ := \argmin_{x \in X} f(x)$. 
                We state the following intermediate results prior to their justifications at the end of the proof. 
                    \item [(a)] $\forall x, y$ it has $\Vert \nabla f(x) - \nabla f(y)\Vert \le \Vert A\Vert^2 L_g \Vert x - y\Vert$. 
                    \item [(b)] There exists uniquely $(t^*, T^*) \in \RR^{m\times n}$ such that for all $\bar x \in X^+$ it has $Ax^+ = t^*, \nabla f(\bar x) = T^*$. In other word, for all minimizers $\bar x$ in $X^+$, $A\bar x$ and, $\nabla f(\bar x)$ are all the same. It would mean $X^+ = \{\bar x : A\bar x = t^*, Cx^* \le d\}$ and, it's also a polyhedron. 
                    \item [(c)] Hoffman error bound for Theorem \ref{thm:q-scnvx-hffmn-eb} applied to polyhedron $X^+$, it has 
                        \dist(x | X^+) \le \theta(A, C)\dist((Ax - t^*, Cx - d) | \{\mathbf 0\}\times \RR^n_-)
                Snatching these two intermediate results, the proof for the overall theorem follows. 
                For all $x \in \RR^n$ denote $\bar x = \Pi_{X^+} x$, using strong convexity of $g$, and $f(x) = g(Ax)$: 
                    f(\bar x) - f(x) - \langle \nabla f(x), \bar x - x\rangle &= 
                    g(A\bar x) - g(x) - \left\langle A^T\nabla g(Ax), \bar x - x\right\rangle
                    &= g(A\bar x) - g(x) - \langle \nabla g(Ax), A\bar x - Ax\rangle
                    &\ge \sigma_g/2\Vert Ax - A\bar x\Vert^2 
                    &\underset{\text{(b)}}{=} \frac{\sigma_g}{2} \Vert Ax - t^*\Vert^2 
                    &\underset{\text{(c)}}{\ge} \frac{\sigma_g}{2\theta(A, C)^2} \Vert x - \bar x\Vert^2. 
                Therefore, the function $f$ is Q-SCNVX, i.e: $f \in \QSCNVX (L_g \Vert A\Vert^2, \sigma_g/\theta(A, C)^2)$. 
                \\\noindent
                \textbf{The Proof of (a)} is direct. 
                    \Vert \nabla f(x) - \nabla f(y)\Vert &= \Vert A^T \nabla g(Ax) - A^T\nabla g(Ay)\Vert
                    &\le \Vert A\Vert \Vert \nabla g(Ax) - \nabla g(Ax)\Vert
                    &\le \Vert A\Vert L_g \Vert Ax - Ay\Vert \le \Vert A\Vert^2 L_g \Vert x - y\Vert. 
                \textbf{The proof of (b)} has some details. 
                The set $X^+$ is a convex and, $f$ takes the same value all over it. 
                Consider any $\bar x_1, \bar x_2 \in X^+$, they have
                    (1/2)(f(\bar x_1) + f(\bar x_2)) &= f((1/2)(\bar x_1 + \bar x_2)) 
                    &= g((1/2)(A\bar x_1 + \bar x_2)) 
                    &= (1/2)(g(A\bar x_1) + g(A \bar x_2))
                    &\le (1/2)g(A \bar x_1) + (1/2)g(A \bar x_2) - \frac{\sigma_g}{8}\Vert A\bar x_1 + A \bar x_2\Vert^2. 
                On the last inequality, we used an equivalent characterization of strong convexity (Theorem \ref{thm:scnvx-eqvs}). 
                The last inequality implies that $0 \le - \Vert A \bar x_1 - A \bar x_2\Vert^2$, hence it must be that $A\bar x_1 = A \bar x_2$, which would mean $\nabla f(\bar x_1) = \nabla f(\bar x_2)$ because $\nabla f(x) = A^T \nabla g(A \bar x)$. 

@@

                Under Assumption \ref{ass:necoara-2019-settings}, assume that $f$ is Q-SCNVX with $\mu_f, L_f$, then the sequence that satisfies Definition \ref{def:projg-alg} has a linear convergence rate. 

@@

                    \item $f \in \mathbb Q$ satisfying Q-Growth, a consequence of Q-SCNVX by Theorem \ref{thm:wcnvx-hierach}. 
